---
title: "**BIOL361** — Conservation Biology '25"
author: Dr James B Dorey, University of Wollongong
output: github_document
urlcolor: blue

editor_options: 
  markdown: 
    wrap: 80

vignette: >
  %\VignetteIndexEntry{BIOL361_25}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<!-- badges: start -->

[![License](https://img.shields.io/badge/license-GPL%20(%3E=%203)-lightgrey.svg?style=flat)](http://www.gnu.org/licenses/gpl-3.0.html)

<!-- badges: end -->

```{r websiteSetUp, eval = FALSE, include=FALSE}
setwd("/Users/jamesdorey/Desktop/Uni/Teaching/BIOL361/Lectures/2025/Github_BIOL361_25/BIOL361_25")
usethis::use_git("jbdorey/BIOL361_25")
  # Do this only once
# Run once to configure your package to use and deploy pkgdown
usethis::use_pkgdown_github_pages()
pkgdown::build_site()
usethis::use_github_action("pkgdown")
usethis::use_git_remote("origin", url = NULL, overwrite = TRUE)
usethis::use_github(private = FALSE)
```

```{r setup, include=FALSE}
library(readr)
```

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


### University of Wollongong

#### **Overview**
This is a simple GitHub page to host some activities for the BIOL361 cohort. It includes the Weeks [four](DoreyPrac1/Prac1_BIOL361.html) and five practicals by James Dorey and some associated files, like the interactive [Richmond Birdwing map](https://jbdorey.github.io/BIOL361_25/Ornithoptera%20richmondia.html).

## Directory
* [Practical four](DoreyPrac1/Prac1_BIOL361.html)
* [Practical five]
* [Birdwing butterfly map](https://jbdorey.github.io/BIOL361_25/Ornithoptera%20richmondia.html)

## Authors

Contributors names and contact info

Dr James Dorey
[@jamesbeedorey.bsky.social]([https://twitter.com/dompizzie](https://bsky.app/profile/jamesbeedorey.bsky.social))

## Version History

* 0.1
    * Initial Release
