---
output: github_document
editor_options: 
  markdown: 
    wrap: 80

vignette: >
  %\VignetteIndexEntry{BIOL361}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
library(readr)
```

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


## **BIOL361** 2025 — Conservation Biology; University of Wollongong

This is a simple GitHub page to host some activities for the BIOL361 cohort

## Directory
* [Birdwing butterfly map](https://jbdorey.github.io/BIOL361_25/Ornithoptera%20richmondia.html)

### Dependencies

* Describe any prerequisites, libraries, OS version, etc., needed before installing program.
* ex. Windows 10

### Installing

* How/where to download your program
* Any modifications needed to be made to files/folders

### Executing program

* How to run the program
* Step-by-step bullets
```
code blocks for commands
```

## Help

Any advise for common problems or issues.
```
command to run if program contains helper info
```

## Authors

Contributors names and contact info

ex. Dr James Dorey
ex. [@jamesbeedorey.bsky.social]([https://twitter.com/dompizzie](https://bsky.app/profile/jamesbeedorey.bsky.social))

## Version History

* 0.1
    * Initial Release
